---
title: "All about you!"
subtitle: "FEMMES 2019"
output: 
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
library(learnr)
library(googledrive)
library(googlesheets4)
library(tidyverse)
library(knitr)

# load data
drive_deauth()
sheets_deauth()
# Session number: 4
ss_url <- "https://docs.google.com/spreadsheets/d/1zBa86oZLSrN1Kuit7apKeyX1a3AQCLIcYkMjiqhwAd0/edit?usp=sharing"
survey <- read_sheet(
  as_id(ss_url), skip = 1, 
  col_names = c("time_stamp", "num_siblings", "fav_color", "height", 
                "shoe_size", "fav_chocolate", "fav_pet", 
                "fav_season", "day_old")
  ) %>%
  select(-time_stamp)
```


## Shoe size and height

First, let's take a look to see if there is a relationship between shoe size 
and heights of respondents.

```{r height-shoe}
ggplot(data = survey, mapping = aes(x = shoe_size, y = height)) + 
  geom_point(color = "purple") +
  labs(title = "Relationship between shoe size and height", 
       x = "Shoe size", 
       y = "Height (inches)")
```

<br>

```{r height-shoe-text}
textInput(inputId = "height-shoe-text", label = "Does there appear to be a relationship between shoe size and height? If yes is the relationship positive or negative?", width = "100%")
```

<br>

The plot above, called a **scatterplot**, was created using a programming 
language called R. You responded to the survey on a Google Form. Your 
responses were saved as a data file that we accessed using this programming 
language, and then we plotted your responses to two questions (shoe size and height) in a scatterplot.

Next, we'll take a closer look at the data collected from the survey, and re-create the plot shown above together, and customize it.

## Data

Take a look at the table below. This is the data we collected from you! Can you 
recognize your own answers? Scroll to the right to see the entire table

```{r data}
survey %>% kable()
```

<br>

This is called a **dataset**. It's made up of rows and columns. Let's think 
about what each row and what each column represents.

```{r row-column}
question("What does each row of the dataset represent?",
    answer("One of you (respondent)", correct = TRUE),
    answer("A question (variable)"),
    allow_retry = TRUE
  )
question("What does each column of the dataset represent?",
    answer("One of you (respondent)"),
    answer("A question (variable)", correct = TRUE),
    allow_retry = TRUE
  )
```

## Plotting

### 

Let's revisit that plot visualizing the relationship between shoe 
size and height one more time.

This time, you get to create the plot! To do so, hit the `Run Code` button.

```{r height-shoe-recreate, exercise=TRUE}
ggplot(data = survey, mapping = aes(x = shoe_size, y = height)) + 
  geom_point() +
  labs(title = "Relationship between shoe size and height", 
       x = "Shoe size", 
       y = "Height (inches)")
```

Yay! You ran your first piece of R code!

Next, we'll break down the plotting code, and go through it line-by-line.

### Step 1. Lay down your canvas

```{r height-shoe-1, exercise=TRUE}
ggplot(data = survey, mapping = aes(x = shoe_size, y = height)) 
```

### Step 2. Represent your data with points

```{r height-shoe-2, exercise=TRUE}
ggplot(data = survey, mapping = aes(x = shoe_size, y = height)) + 
  geom_point()
```

### Step 3. Label your plot

```{r height-shoe-3, exercise=TRUE}
ggplot(data = survey, mapping = aes(x = shoe_size, y = height)) + 
  geom_point() + 
  labs(title = "Relationship between shoe size and height", 
       x = "Shoe size", 
       y = "Height (inches)")
```

```{r height-shoe-3-text}
textInput(inputId = "height-shoe-3-text", label = "Can you spot the small difference between the plot you just made and the first plot we saw?", width = "100%")
```

```{r change-which-line}
question("Which line of code above would you need to update to make this plot look like the first plot we saw?",
    answer("Line 1"),
    answer("Line 2", correct = TRUE),
    answer("Line 3"),
    answer("Line 4"),
    answer("Line 5"),
    allow_retry = TRUE
  )
```

### Step 4. Customize

Lastly, we'll change the color of the points. To do so, we add a new argument 
to the `geom_point()` function. Let's make the points purple.

```{r height-shoe-4, exercise=TRUE}
ggplot(data = survey, mapping = aes(x = shoe_size, y = height)) + 
  geom_point(color = "purple") + 
  labs(title = "Relationship between shoe size and height", 
       x = "Shoe size", 
       y = "Height (inches)")
```

### Your turn!

Now pick a different color, and fill in the blank below with the name of the 
color. 

If you need inspiration for a color, you can pick one from <a href="http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf" target="_blank">here</a>. Note that the 
name of the color needs to be spelled exactly the same as it appears on the 
linked document.

```{r height-shoe-5, exercise=TRUE}
ggplot(data = survey, mapping = aes(x = shoe_size, y = height)) + 
  geom_point(color = "____") + 
  labs(title = "Relationship between shoe size and height", 
       x = "Shoe size", 
       y = "Height (inches)")
```

## Shoe size and number of siblings

### 

```{r shoe-sibling, exercise=TRUE}
ggplot(data = survey, mapping = aes(x = shoe_size, y = num_siblings)) + 
  geom_point(color = "purple")
```

<br>

```{r shoe-sibling-text}
textInput(inputId = "shoe-sibling-text", label = "Does there appear to be a relationship between shoe size and number of siblings? If yes is the relationship positive or negative?", width = "100%")
```

### Your turn!

The labels for the plot are missing in the code below. Enter the appropriate 
labels, and run your code.

```{r shoe-sibling-labels, exercise=TRUE}
ggplot(data = survey, mapping = aes(x = shoe_size, y = num_siblings)) + 
  geom_point(color = "purple")  + 
  labs(title = "____", 
       x = "____", 
       y = "____")
```

PS: You can also change the point colors if you want.

## Favorite color

### Bar plot

The following visualization is called a **bar plot**, it's used to visualize 
**categorical** data.

```{r fav-color}
ggplot(data = survey, mapping = aes(x = fav_color, fill = fav_color)) + 
  geom_bar() +
  labs(x = "Color", title = "Favorite color")
```

<br>

```{r fav-color-text}
textInput(inputId = "fav-color-text", label = "What is the most popular color among the respondents?", width = "100%")
```

### Add some color

Let's add some color to our plot.

```{r fav-color-color, exercise=TRUE}
color_pallete <- c(
  "Red" = "red",
  "Blue" = "blue",
  "Green" = "darkgreen",
  "Pink" = "pink",
  "Other" = "orange"
)

ggplot(data = survey, mapping = aes(x = fav_color, fill = fav_color)) + 
  geom_bar() +
  labs(x = "Color", title = "Favorite color") +
  scale_fill_manual(name = "Color", 
                    values = color_pallete, 
                    limits = names(color_pallete))
```

### Your turn!

Update the code below so the `Other` category is colored gray instead of orange.

```{r fav-color-change, exercise=TRUE}
color_pallete <- c(
  "Red" = "red",
  "Blue" = "blue",
  "Green" = "darkgreen",
  "Pink" = "pink",
  "Other" = "orange"
)

ggplot(data = survey, mapping = aes(x = fav_color, fill = fav_color)) + 
  geom_bar() +
  labs(x = "Color", title = "Favorite color") +
  scale_fill_manual(name = "Color", 
                    values = color_pallete, 
                    limits = names(color_pallete))
```

## Favorite chocolate

### 

We'll use another bar plot to visualize your favorite chocolate choices.

Note the last line of the code, which **flip**s the **coord**inates, and makes 
the bars horizontal.

```{r fav-chocolate, exercise = TRUE}
ggplot(data = survey, mapping = aes(x = fav_chocolate)) + 
  geom_bar() +
  labs(x = "", title = "Favorite chocolate") + 
  coord_flip()
```

<br>

```{r fav-chocolate-text}
textInput(inputId = "fav-chocolate-text", label = "What is the most popular chocolate among the respondents?", width = "100%")
```

### Your turn!

Update the code below to color the bars according to the various chocolate 
colors. For the "I don't like chocolate" category you can use any color you 
like. Refer to <a href="http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf" target="_blank">this document</a> for names of colors in R.

```{r fav-chocolate-colors, exercise = TRUE}
color_pallete <- c(
  "White chocolate" = "___",
  "Milk chocolate" = "___",
  "Dark chocolate" = "___",
  "I don't like chocolate" = "___"
)

ggplot(data = survey, mapping = aes(x = fav_chocolate, fill = fav_chocolate)) + 
  geom_bar() +
  labs(x = "", title = "Favorite chocolate") + 
  coord_flip() +
  scale_fill_manual(name = "Color", 
                    values = color_pallete, 
                    limits = names(color_pallete))
```
